---
output: github_document

---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%",
  dpi = 400,
  fig.align = "center"
)
```

# mediocrethemes

<!-- badges: start -->

<!-- badges: end -->

This package provides not particularly nice and, hopefully, not particularly ugly ggplot themes.

## Installation

You can install the development version of `mediocrethemes` from [GitHub](https://github.com/vincentbagilet/mediocrethemes) with:

```{r eval=FALSE}
# install.packages("pak")
pak::pak("vincentbagilet/mediocrethemes")
```

Note that you may need to restart your R session once the installation is complete to be able to use the package. You will also need an active internet connection the first time you call `set_mediocre_all`, `theme_mediocre`, or `theme_idid`.

## Usage

This package provides both `ggplot` themes and a breadth of color palettes. 

The most useful feature of the package is the `set_mediocre_all` function. It allows users to set the theme and color palette for all plots in a document:

```{r set_mediocre_all, warning=FALSE}
library(ggplot2)
library(mediocrethemes)

set_mediocre_all(pal = "idid", theme = theme_idid)

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
  geom_col() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

This can be undone with the `unset_mediocre_all` function.

```{r unset_mediocre_all}
unset_mediocre_all()
```

Users also can set the theme and color palette independently.

```{r base_graph}
ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
  geom_point() +
  theme_idid() +
  scale_mediocre_d() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

## Examples

### General examples

A couple of example plots obtained with this theme:

```{r examples, echo=FALSE}
set_mediocre_all(pal = "idid", theme = theme_idid)

make_example_plots <- function() {
  g1 <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(g1)

  g2 <- ggplot(data = ggplot2::mpg, aes(x = drv)) +
    geom_bar(aes(fill = factor(year)), position = "dodge") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(g2)
  
  g3 <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_point(aes(color = factor(year))) +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(g3)
  
  g4 <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = drv)) +
    geom_col() +
    geom_vline(xintercept = 15, linewidth = 1) +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(g4)
  
  g5 <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_point() +
    geom_smooth(method = 'loess', formula = 'y ~ x') +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(g5)
  
  g6 <- ggplot(data = ggplot2::mpg, aes(x = cty)) +
      geom_density() +
      labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(g6)
  
  df <- data.frame(
    x = rnorm(10000),
    y = rnorm(10000)
  )
  
  g7 <- ggplot(df, aes(x, y)) +
    geom_hex() +
    coord_fixed() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(g7)
  
  g8 <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_point() +
    facet_wrap(~ year) +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle") 
  
  print(g8)
}

make_example_plots()
```

### mediocre theme

The package has been updated with a more modern theme (`idid`) but the initial theme (`mediocre`) is still available (and remains the default). Here are the same example graphs but with the original `mediocre` theme.

```{r examples_mediocre, echo=FALSE}
set_mediocre_all()

make_example_plots()
```

### Additional palettes

Note that additional palettes are available: `r mediocrethemes::colors_table[[1]]`. 

```{r palettes, echo=FALSE}
for (palette in mediocrethemes::colors_table[[1]][-1]) {
  set_mediocre_all(pal = palette, theme_idid)

  graph <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
      geom_col() +
      labs(title = "A very nice title", subtitle = "A disappointing subtitle")

  print(paste("set_mediocre_all(pal = '", palette, "')", sep = ""))
  print(graph)
}
```

Most palettes are divergent but can be turned into two gradient palettes, as described in the [vignette](mediocrethemes.html).

