---
output: github_document

---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%",
  dpi = 400,
  fig.align = "center"
)
```

# mediocrethemes

<!-- badges: start -->
<!-- badges: end -->

This package provides not particularly nice and, hopefully, not particularly ugly ggplot themes.

## Installation

You can install the development version of `mediocrethemes` from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("vincentbagilet/mediocrethemes")
```

Note that you may need to restart your R session once the installation is complete to be able to use the package. 

## Usage

This package provides both a ggplot theme and a color palette. Users can set the theme and color palette independently.

```{r base_graph}
library(ggplot2)
library(mediocrethemes)

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_point() +
    theme_mediocre() +
    scale_mediocre_d() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

Users can also set the theme and color palette for all plots in a document with the function `set_mediocre_all` placed at the top of their document:

```{r set_mediocre_all}
set_mediocre_all()

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

## Examples

### General examples

A couple of example plots obtained with this theme:

```{r examples, echo=FALSE}
ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = drv)) +
    geom_bar(aes(fill = factor(year)), position = "dodge") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = drv)) +
  geom_col() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
  geom_point() +
  geom_smooth() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty)) +
    geom_density() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

df <- data.frame(
  x = rnorm(10000),
  y = rnorm(10000)
)

ggplot(df, aes(x, y)) +
  geom_hex() +
  coord_fixed() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
  geom_point() +
  facet_wrap(~ year) +
  theme_mediocre() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle") 
```

### Additional palettes

Note that additional palettes are available.

#### rainbow

```{r rainbow, echo=FALSE}
set_mediocre_all(pal = "rainbow")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = drv)) +
    geom_bar(aes(fill = factor(year)), position = "dodge") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = drv)) +
  geom_col() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

df <- data.frame(
  x = rnorm(10000),
  y = rnorm(10000)
)

ggplot(df, aes(x, y)) +
  geom_hex() +
  coord_fixed() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

#### coty

A (tentatively) colorblind friendly palette, based on a NPR map.

```{r coty, echo=FALSE}
set_mediocre_all(pal = "coty")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = drv)) +
    geom_bar(aes(fill = factor(year)), position = "dodge") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = drv)) +
  geom_col() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

df <- data.frame(
  x = rnorm(10000),
  y = rnorm(10000)
)

ggplot(df, aes(x, y)) +
  geom_hex() +
  coord_fixed() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

#### hotcold

```{r hotcold, echo=FALSE}
set_mediocre_all(pal = "hotcold")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = drv)) +
    geom_bar(aes(fill = factor(year)), position = "dodge") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = drv)) +
  geom_col() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

df <- data.frame(
  x = rnorm(10000),
  y = rnorm(10000)
)

ggplot(df, aes(x, y)) +
  geom_hex() +
  coord_fixed() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

#### blackandwhite

```{r blackandwhite, echo=FALSE}
set_mediocre_all(pal = "blackandwhite")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = drv)) +
    geom_bar(aes(fill = factor(year)), position = "dodge") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = drv)) +
  geom_col() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

df <- data.frame(
  x = rnorm(10000),
  y = rnorm(10000)
)

ggplot(df, aes(x, y)) +
  geom_hex() +
  coord_fixed() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```
