---
output: github_document

---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%",
  dpi = 400,
  fig.align = "center"
)
```

# mediocrethemes

<!-- badges: start -->
<!-- badges: end -->

This package provides not particularly nice and, hopefully, not particularly ugly ggplot themes.

## Installation

You can install the development version of `mediocrethemes` from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("vincentbagilet/mediocrethemes")
```

Note that you may need to restart your R session once the installation is complete to be able to use the package. You will also need an active internet connection the first time you call `set_mediocre_all` or `theme_mediocre`.

## Usage

This package provides both a ggplot theme and a color palette.

Users can set the theme and color palette for all plots in a document with the function `set_mediocre_all` placed at the top of their document:

```{r set_mediocre_all}
library(ggplot2)
library(mediocrethemes)

set_mediocre_all()

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

Users also can set the theme and color palette independently.

```{r base_graph}
ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_point() +
    theme_mediocre() +
    scale_mediocre_d() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

## Examples

### General examples

A couple of example plots obtained with this theme:

```{r examples, echo=FALSE}
ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = drv)) +
    geom_bar(aes(fill = factor(year)), position = "dodge") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_point(aes(color = factor(year))) +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = drv)) +
  geom_col() +
  geom_vline(xintercept = 15) +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
  geom_point() +
  geom_smooth(method = 'loess', formula = 'y ~ x') +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty)) +
    geom_density() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")

df <- data.frame(
  x = rnorm(10000),
  y = rnorm(10000)
)

ggplot(df, aes(x, y)) +
  geom_hex() +
  coord_fixed() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
  geom_point() +
  facet_wrap(~ year) +
  theme_mediocre() +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle") 
```

### Additional palettes

Note that additional palettes are available. 
Most palettes are divergent and can be turned into two gradient palettes. This is done by splitting a divergent palette in the middle, and use either the set of colors on the right or on the left (flipped to get light colors for small values).

#### rainbow

```{r rainbow, echo=FALSE}
plot_all_examples <- function(pal) {
  set_mediocre_all(pal = pal)
  
  plot1 <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(plot1)
  
  plot2 <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
      geom_col() +
      labs(title = "A very nice title", subtitle = "A disappointing subtitle") 
  
  print(plot2)
  
  plot3 <- ggplot(data = ggplot2::mpg, aes(x = drv)) +
      geom_bar(aes(fill = factor(year)), position = "dodge") +
      labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(plot3)
  
  plot4 <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = drv)) +
    geom_col() +
    geom_vline(xintercept = 15) +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle") 
  
  print(plot4)
  
  df <- data.frame(
    x = rnorm(10000),
    y = rnorm(10000)
  )
  
  plot5 <- ggplot(df, aes(x, y)) +
    geom_hex() +
    coord_fixed() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle") 
  
  print(plot5)
  
  if (pal != "blackandwhite") {
    plot6 <- ggplot(data = ggplot2::diamonds, aes(x = price, fill = color)) +
    geom_histogram(bins = 30) +
    scale_mediocre_d(pal = pal, gradient = "left") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
  
  print(plot6)
  
  plot7 <- ggplot(data = ggplot2::diamonds, aes(x = price, fill = color)) +
    geom_histogram(bins = 30) +
    scale_mediocre_d(pal = pal, gradient = "right") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle") 
  
  print(plot7)
  } 
} 

plot_all_examples(pal = "rainbow")
```

#### coty

A (tentatively) colorblind friendly palette, based on [a NPR map](https://www.npr.org/2016/04/18/474256366/why-americas-schools-have-a-money-problem?t=1614618030346).

```{r coty, echo=FALSE}
plot_all_examples(pal = "coty")
```

#### hotcold

```{r hotcold, echo=FALSE}
plot_all_examples(pal = "hotcold")
```

#### blackandwhite

```{r blackandwhite, echo=FALSE}
plot_all_examples(pal = "blackandwhite")
```
