---
title: "Using mediocrethemes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using mediocrethemes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # fig.path = "man/figures/README-",
  out.width = "70%",
  dpi = 400,
  fig.align = "center",
  dev = "png",
  fig.width = 7,
  fig.height = 5
)
```

This vignette gives a brief introduction to the `mediocrethemes` package. After installing the package from GitHub, load the package. For simplicity, we also load packages from the tidyverse.

```{r setup, message = FALSE, warning = FALSE}
library(mediocrethemes)
```

# Main use

## The easiest way to use this theme

The easiest way to use the `mediocrethemes` package is through the `set_mediocre_all` function. It enables to set both the theme and the color scale for all graphs in a document. The user can call this function at the beginning of the document. Then, plots can be created using the standard ggplot commands.

```{r set_mediocre_all}
set_mediocre_all()

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
    geom_col() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

This function takes several arguments: `pal`, `background` and `second_pair`.

### Changing the palette

The following palettes are available: `r mediocrethemes::colors_table[[1]]`. A palette defines the color of the theme and the color scale used in the graphs. Here is a comparison of the different palettes:

```{r palettes, echo=FALSE}
for (palette in mediocrethemes::colors_table[[1]]) {
  print(palette)
  set_mediocre_all(pal = palette)

  graph <- ggplot(data = ggplot2::mpg, aes(x = cty, y = displ, fill = manufacturer)) +
      geom_col() +
      labs(title = "A very nice title", subtitle = "A disappointing subtitle")

  print(graph)
}
```

### Setting a background

Users can also easily set a background for all their plots by setting the parameter `background` to `TRUE`. The color of the background is predefined to  fit nicely the theme palette. One can of course still modify the background color by adding a layer to the ggplot theme: `theme(plot.background = element_rect(fill = "red"))`.

```{r background}
set_mediocre_all(background = TRUE)

ggplot(data = ggplot2::mpg, aes(x = cty, y = displ)) +
    geom_point() +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

### Using another pair of colors

Oftentimes, users build graphs with two categories.

```{r}
set_mediocre_all()
```


```{r echo=FALSE}
ggplot(data = ggplot2::mpg, aes(x = drv)) +
    geom_bar(aes(fill = factor(year)), position = "dodge") +
    labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

In a same project, they may have to consider two sets of pairs, *eg* for two different production years and the number of cylinders in a car. They may not want to use the same color pair since the colors would not represent the same thing. They can therefore set the `second_pair` parameter to `TRUE`.

```{r}
set_mediocre_all(second_pair = TRUE)
```

```{r echo=FALSE}
ggplot(data = ggplot2::presidential, aes(x = party)) +
  geom_bar(aes(fill = party), position = "dodge") +
  labs(title = "A very nice title", subtitle = "A disappointing subtitle")
```

## Underlying functions

The function `set_all_mediocre` is built on the `theme_mediocre` and `scale_mediocre_d`/`scale_mediocre_c` functions. The former, `theme_mediocre` sets the theme and a baseline color and the later set scales.

# Acessing the color used in a scale

All the colors used are stored in the table `colors_table`:

```{r}
colors_table
```

For instance, one can access the "base" color for the palette "coty", in a HEX format, using the following command:

```{r}
mediocrethemes::colors_table[[6, "base"]]
```




